Flowchart of Current Algorithm

### 2008-10-28 docs/flowchart/flowchart.tex
addressed Mike's MaringPars about the in/out notation of the edge states in the advect base descriptions.  Fixed one typo, where the (rho h)0 edge states had an "out" superscript - they should not have this.
-The reason why the rho0 edge states have an "out" is because we compute these states within advect_base_dens.

-The reason why the rhoh0 edge states have neither "in" nor "out" is because we compute them within the advect_base_pres and advect_base_enthalpy subroutines and do not pass them out since they aren't used outside of the subroutine (for now).

\item[plane-parallel:] We discretize equation the base state density evolution 
equation (paper III; eq.~[29]) without the $\etarho$ term,
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
\enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
to compute the new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ]
         \nonumber \enskip,
\end{eqnarray}
\MarginPar{why is the notation for the edge state ${{\rho}_0}^{\outp,\nph}$? shouldn't
           it be ${{\rho}_0}^{\inp,\nph}$?}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A.

@@

\item[plane-parallel:] First we compute a cell-centered $\psi^\outp$ using
\begin{equation}
 \psi_j^\outp = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^\inp + \eta_{\rho,j+\myhalf}^\inp\right) g \enskip .
\end{equation}
Then, we discretize the base state pressure evolution equation (paper III; eq.~[31]),
\begin{equation}
\frac{\partial p_0}{\partial t} = 
-w_0 \frac{\partial p_0}{\partial r} + \psi \enskip ,
\label{eq:p0upd_new}
\end{equation}
to compute the new base state pressure,
\begin{equation}
p_{0,j}^\outp = p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\outp 
\enskip,
\end{equation}
\MarginPar{shouldn't the edge states for $p_0$ have a $\inp$ or $\outp$ superscript?}
where the interface states are again found via the procedure described
in paper II, Appendix A.

@@

\item[plane-parallel:] We discretize
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} = -\nabla\cdot\left[(\rho h)_0w_0\er\right] 
+ \psi \enskip ,
\end{equation}
to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r}
\left\{ \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j+\myhalf} -  
         \left[ {(\rho h)_0}^{\outp,\nph} {w_0}^{\inp}\right]_{j-\myhalf} \right\}
+ \dt\psi_j^{\inp} \enskip ,
\end{equation}
\MarginPar{why is the notation for the edge state ${{\rho h}_0}^{\outp,\nph}$? shouldn't
           it be ${{\rho h}_0}^{\inp,\nph}$?}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in 
the forcing for the interface state calculation, but is used in the update.

>>>>

\item[plane-parallel:] We discretize equation the base state density evolution 
equation (paper III; eq.~[29]) without the $\etarho$ term,
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
\enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
to compute the new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ]
         \nonumber \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A.

@@

\item[plane-parallel:] First we compute a cell-centered $\psi^\outp$ using
\begin{equation}
 \psi_j^\outp = \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^\inp + \eta_{\rho,j+\myhalf}^\inp\right) g \enskip .
\end{equation}
Then, we discretize the base state pressure evolution equation (paper III; eq.~[31]),
\begin{equation}
\frac{\partial p_0}{\partial t} = 
-w_0 \frac{\partial p_0}{\partial r} + \psi \enskip ,
\label{eq:p0upd_new}
\end{equation}
to compute the new base state pressure,
\begin{equation}
p_{0,j}^\outp = p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\outp 
\enskip,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.

@@

\item[plane-parallel:] We discretize
\begin{equation}
\frac{\partial (\rho h)_0}{\partial t} = -\nabla\cdot\left[(\rho h)_0w_0\er\right] 
+ \psi \enskip ,
\end{equation}
to compute the new base state enthalpy,
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} - \frac{\dt}{\Delta r}
\left\{ \left[ {(\rho h)_0}^{\nph} {w_0}^{\inp}\right]_{j+\myhalf} -  
         \left[ {(\rho h)_0}^{\nph} {w_0}^{\inp}\right]_{j-\myhalf} \right\}
+ \dt\psi_j^{\inp} \enskip ,
\end{equation}
where the interface states are again found via the procedure described
in paper II, Appendix A.  Note that the $\psi$ term is not included in 
the forcing for the interface state calculation, but is used in the update.
